### 2019-10-29 Action letter.Rmd
Reviewer 2 Comment 15

10. Please define measurement invariance (parentheses is fine - e.g., measurement equivalence) for the less statistically trained reader.

11. The authors need to walk the reader through the tables better. The results section and tables need to be easier to navigate and understand. It is clear you did a tremendous amount of work on these analyses, and I want all readers to be able to follow the results very easily.
12. The findings on line 336 don't make sense given the previous line. The authors need to introduce all of the outcomes discussed in line 336: With regard to child effects, in line with hypotheses, the intercept of the cross-lagged
335 effect of emotional adjustment on maternal warmth was positive and significant (Table 2).
336 Thus, when children displayed better emotional adjustment than usual in one year, their
337 mothers displayed more anger and inductive reasoning, but also more warmth, than usual in
338 the next year.
13. Line 383 you use "discipline" for the first time. Do you mean demandingness?
14. I don't understand your argument in the discussion around the within family significant association between consistency and adjustment. You're saying that because you found tween family level correlations but not within family correlations that this suggests other correlated variables like economic hardship do not explain this association? What do your findings mean?
15. Regarding the direction of effects, is your conclusion that child effects are stronger than parenting effects driven entirely by the size of the coefficient? Did you conduct any tests to compare the two models and their coefficients? I assume parenting and child effects were run separately considering they are modeled as predicting different outcomes?
16. Can you test for non-linear effects of quantitative involvement on emotional adjustment? Your explanation that excessive involvement leads to maladjustment makes sense, but one would expect a u-shaped curve in which adjustment is highest at an optimal middle ground of involvement. You could also test for mean differences in emotional adjustment for children with highly involved parents versus less involved parents. It could be, as you argue in the next section of the discussion, that the effect of involvement on emotional adjustment is stronger when only one parent is involved because there is less variability in children's adjustment when both parents are highly involved. This would help test your two suggested explanations.

>>>>

\rc{10. Please define measurement invariance (parentheses is fine - e.g., measurement equivalence) for the less statistically trained reader.}

We have addressed this comment by including the following explanation:

> (i.e., to assume that the factor loadings of each construct are the same across time points)

11. The authors need to walk the reader through the tables better. The results section and tables need to be easier to navigate and understand. It is clear you did a tremendous amount of work on these analyses, and I want all readers to be able to follow the results very easily.

12. The findings on line 336 don't make sense given the previous line. The authors need to introduce all of the outcomes discussed in line 336: With regard to child effects, in line with hypotheses, the intercept of the cross-lagged

335 effect of emotional adjustment on maternal warmth was positive and significant (Table 2).
336 Thus, when children displayed better emotional adjustment than usual in one year, their
337 mothers displayed more anger and inductive reasoning, but also more warmth, than usual in
338 the next year.

\rc{13. Line 383 you use "discipline" for the first time. Do you mean demandingness?}

Apologies for the oversight; we simply meant to say Inductive Reasoning. We have corrected this typo in the revision.

\rc{14. I don't understand your argument in the discussion around the within family significant association between consistency and adjustment. You're saying that because you found tween family level correlations but not within family correlations that this suggests other correlated variables like economic hardship do not explain this association? What do your findings mean?}

With all due respect, we do not entirely understand the Reviewer's comment, but we take it to mean that our argumentation in this paragraph was unclear. In the revision, we have rewritten this section as follows:

> On average, we found no support for within-family predictive links between consistency and adjustment, but we did find support for between-family level correlations. Between-family level correlations can have different causes: They can reflect the consolidated influence of predictive effects that occurred prior to the study, or alternatively, the influence of third variables that impact both constructs. The fact that our study included children from a very young age casts doubt on the former explanation. It seems more likely that third variables explain these associations. Economic hardship, for instance, undermines parents' capacity for consistent parenting, as well as children's socio-emotional adjustment [@mcloydImpactEconomicHardship1990]. This finding means that we should reflect critically on causal interpretations of prior research that did not control for stable between-family differences [e.g., @brandPerceivedParentalInconsistency1990].

15. Regarding the direction of effects, is your conclusion that child effects are stronger than parenting effects driven entirely by the size of the coefficient? Did you conduct any tests to compare the two models and their coefficients? I assume parenting and child effects were run separately considering they are modeled as predicting different outcomes?
16. Can you test for non-linear effects of quantitative involvement on emotional adjustment? Your explanation that excessive involvement leads to maladjustment makes sense, but one would expect a u-shaped curve in which adjustment is highest at an optimal middle ground of involvement. You could also test for mean differences in emotional adjustment for children with highly involved parents versus less involved parents. It could be, as you argue in the next section of the discussion, that the effect of involvement on emotional adjustment is stronger when only one parent is involved because there is less variability in children's adjustment when both parents are highly involved. This would help test your two suggested explanations.

### 2019-10-29 Paper_shortened_pdf.Rmd
Reviewer 2 Comment 15

We calculated mean scores for all of the study variables. Scale descriptive statistics are provided in Supplementary Table 1, and scale correlations are provided in Supplementary Table 2. We deemed it defensible to assume measurement invariance, as the difference in fit between structurally invariant models, and metrically invariant models, was smaller than .01 on all conventional fit indices: RMSEA, CFI, and TLI (see Supplementary Table 3).

@@

With regard to the moderation of child effects by quantitative involvement, we found that the effect of adjustment on maternal warmth was negatively attenuated when parents' joint involvement was higher, and also when mothers' relative involvement was greater compared to fathers. We found no effects for consistency. For inductive reasoning, we found that that the cross-lagged effect of adjustment on maternal inductive reasoning was negatively attenuated when both parents' joint involvement was higher. In other words, when both parents were  more involved, the cross-lagged effect of children's adjustment on maternal discipline was more negative. Adjustment was also more negatively predictive of fathers' inductive reasoning when mothers were relatively more involved than fathers. Thus, in families where mothers were more involved than fathers, children's increased emotional adjustment more strongly predicted decreased paternal reasoning - and conversely, decreased emotional adjustment predicted increased paternal reasoning. We found no moderating effects for anger.

@@

We found partial support for positive associations of parental consistency with emotional adjustment, primarily at the between-family level: children in families with highly consistent parents tended to be more emotionally well-adjusted. We found the predicted within-family correlations for mothers', but not fathers', consistency. On average, we found no support for within-family predictive links between consistency and adjustment. It is interesting that we found only between-family links and no predictive effects for consistency: Between-family level correlations can reflect the consolidated influence of predictive effects at an earlier age, or alternatively, the influence of third variables that impact both constructs. Economic hardship, for instance, undermines parents' capacity for consistent parenting, as well as children's socio-emotional adjustment [@mcloydImpactEconomicHardship1990]. The fact that we observed no within-family predictive effects, despite including children from a very young age, casts doubt on the former explanation, and on causal interpretations of prior research that did not control for stable between-family differences [@brandPerceivedParentalInconsistency1990].

>>>>

We calculated mean scores for all of the study variables. Scale descriptive statistics are provided in Supplementary Table 1, and scale correlations are provided in Supplementary Table 2. We deemed it defensible to assume metric measurement invariance (i.e., to assume that the factor loadings of each construct are the same across time points), as the difference in fit between structurally invariant models, and metrically invariant models, was smaller than .01 on all conventional fit indices: RMSEA, CFI, and TLI (see Supplementary Table 3).

@@

With regard to the moderation of child effects by quantitative involvement, we found that the effect of adjustment on maternal warmth was negatively attenuated when parents' joint involvement was higher, and also when mothers' relative involvement was greater compared to fathers. We found no effects for consistency. For inductive reasoning, we found that that the cross-lagged effect of adjustment on maternal inductive reasoning was negatively attenuated when joint involvement was higher. Adjustment was also more negatively predictive of fathers' inductive reasoning when mothers were relatively more involved than fathers. Thus, in families where mothers were more involved than fathers, children's increased emotional adjustment more strongly predicted decreased paternal reasoning - and conversely, decreased emotional adjustment predicted increased paternal reasoning. We found no moderating effects for anger.

@@

We found partial support for positive associations of parental consistency with emotional adjustment, primarily at the between-family level: children in families with highly consistent parents tended to be more emotionally well-adjusted. We found the predicted within-family correlations for mothers', but not fathers', consistency. On average, we found no support for within-family predictive links between consistency and adjustment, but we did find support for between-family level correlations. Between-family level correlations can have different causes: They can reflect the consolidated influence of predictive effects that occurred prior to the study, or alternatively, the influence of third variables that impact both constructs. The fact that our study included children from a very young age casts doubt on the former explanation. It seems more likely that third variables explain these associations. Economic hardship, for instance, undermines parents' capacity for consistent parenting, as well as children's socio-emotional adjustment [@mcloydImpactEconomicHardship1990]. This finding means that we should reflect critically on causal interpretations of prior research that did not control for stable between-family differences [e.g., @brandPerceivedParentalInconsistency1990].
